Output Summary

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Add Yr2 & Yr3 ocean surv to MCMC diags again
Why not -- these aren't key parameters

# Year 2 ocean survival
# L1 = "Year 2 Ocean Survival"
# L2 = c("Mean")
# base = c("mu_phi_O1_O2[origin,pop]")
# match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
# tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
# tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
# diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
# summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Year 2 ocean survival
# L1 = "Year 3 Ocean Survival"
# L2 = c("Mean")
# base = c("mu_phi_O2_O3[origin,pop]")
# match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
# tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
# tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
# diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
# summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

>>>>

# Year 2 ocean survival
L1 = "Year 2 Ocean Survival"
L2 = c("Mean")
base = c("mu_phi_O1_O2[origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))

# Year 2 ocean survival
L1 = "Year 3 Ocean Survival"
L2 = c("Mean")
base = c("mu_phi_O2_O3[origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
tmp_diags = lapply(1:length(match), function(i) summarize_posterior(match[i], L1 = L1, L2 = L2[i]))
tmp_summ = lapply(tmp_diags, function(i) summarize_diags(i))
diags_out = rbind(diags_out, do.call(rbind, tmp_diags))
summs_out = rbind(summs_out, do.call(rbind, tmp_summ))
